---
title: "Practical Exam"
author: "Luigi Echaveria"
date: "2024-03-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#A.
#1. Find out, in a single command, which columns of warpbreaks are either numeric or integer.
```{r}
warpbreaks

numeric_columns <- sapply(warpbreaks, is.numeric)
integer_columns <- sapply(warpbreaks, is.integer)
```

#2. How many observations does it have?
```{r}
nrow(warpbreaks)
```

#3. Is numeric a natural data type for the columns which are stored as such? Convert to integer when necessary.
```{r}
numeric <- as.integer(warpbreaks$breaks)
```

#4. Error messages in R sometimes report the underlying type of an object rather than the user-level class. Derive from the following code and error message what the underlying type.
```{r}
x <- c("1", "2", "3", "4")
x <- as.numeric(x)
y <- x + 1
```
#Error message:
#Error in x + 1 : non-numeric argument to binary operator


#B
#1. Read the complete file using readLines.
```{r}
ReadExample <- readLines("exampleFile.txt")
ReadExample
```

#2. Separate the vector of lines into a vector containing comments and a vector containing the data.
```{r}
comments <- grepl("^#", ReadExample) 
comments_vec <- ReadExample[comments] 
data_vec <- ReadExample[!comments]

cat("Comments:\n")
print(comments_vec)
cat("\nData:\n")
print(data_vec)
```

#3. Extract the date from the first comment line and display on the screen “It was created data.”
```{r}

```

#4. Read the data into a matrix as follows.
#a. Split the character vectors in the vector containing data lines by semicolon (;) using strsplit.
```{r}

```

#b. Find the maximum number of fields retrieved by split. Append rows that are shorter with NA's.
```{r}

```

#c. Use unlist and matrix to transform the data to row-column format.
```{r}

```

#d. From comment lines 2-4, extract the names of the fields. Set these as colnames for the matrix you just created.
```{r}

```
